Compositional equivalences based on Open pNets

### 2020-03-04 2016-Weak-FH-Bisim/WeakBisim.tex
details 8'''

So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and we will get e.g. the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$
\medskip

@@

>>>>

So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the Post of the weak OT $WI_{3}$ is $ {Post_{456}}^*\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and $Post(WI_{3'})$ is $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
\medskip

@@

  $ WI_4(n) = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$

$ WI_{8'''}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
         \ \forall n\ge 1$
